---
title: "firstTry"
author: "Tim Kelso"
date: "05/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(generativeart)
source('../scripts/00-ttrc_style.R')
```

The package works with a specific directory structure that fits my needs best. 
The first step is to create it with setup_directories(). 
All images are saved by default in img/everything/. 
I use img/handpicked/ to choose the best ones. 
In logfile/ you will find a csv file that saves the file_name, the seed and the used formula

``` {r package_setup}
# set the paths
IMG_DIR <- "../img/"
IMG_SUBDIR <- "everything/"
IMG_SUBDIR2 <- "handpicked/"
IMG_PATH <- paste0(IMG_DIR, IMG_SUBDIR)

LOGFILE_DIR <- "../logfile/"
LOGFILE <- "logfile.csv"
LOGFILE_PATH <- paste0(LOGFILE_DIR, LOGFILE)

# create the directory structure
generativeart::setup_directories(IMG_DIR, IMG_SUBDIR, IMG_SUBDIR2, LOGFILE_DIR)
```

You can create as many images as you want by setting nr_of_img.
For every image a seed is drawn from a number between 1 and 10000.
This seed determines the random numbers in the formula.
You can choose between cartesian and polar coordinate systems by setting polar = TRUE or polar = FALSE
You can choose the colors with color = 'black' and background_color = 'hotpink'
You can save the output image in various formats. Default is png, the alternatives are defined by the device options of ggplot::ggsave().
the formula is a list()

``` {r create_art1}
my_formula <- list(
  x = quote(runif(1, -1, 1) * x_i^3 - sin(y_i^2)),
  y = quote(runif(1, -1, 1) * y_i^2 - cos(x_i^2))
)

# call the main function to create five images with a polar coordinate system
generativeart::generate_img(formula = my_formula, nr_of_img = 3, polar = TRUE, filetype = "png", color = "black", background_color = QTcolours_bckgrnd$key[4])
```